Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-15 resex.tex
Another intermediate step in revision of random results. Emittance growth rates to be verified.

Qualitatively, this behavior could be also confirmed experimentally
during the 2017 experiments. Here excitation amplitude dependent
emittance growth was only recorded in the plane of excitation with all
excitation amplitude dependent emittance growth rates in a comparable
range. As example the relative horizontal and vertical emittance for
pulsing in V and in H+V are depicted in Fig.~\ref{fig:ranexp}. Note
that as expected from simulations and despite the large excitation
amplitude dependent emittance growth, the growth rates stays
constant. There is explicitly no fast adjustment phase succeeded by a
new equilibrium state as observed for the 7th- and \tenthtp.

>>>>

The effects of random excitation were measured during the 2017
experiments. Increasing emittance growth with excitation amplitude was
recorded only in the plane of excitation. Horizontal and vertical
emittance growth rates for a given amplitude were comparable. As an
example, the relative horizontal and vertical emittances during V and
H+V pulsing are illustrated in Fig.~\ref{fig:ranexp}. In addition, the
excitations translated into constant growth rates. In particular,
there was no adjustment phase followed by an equilibrium state, as
observed during 7th- and \tenthtp. The qualitative behavior of
emittances predicted in simulations was therefore confirmed. However,
the calculations could only roughly reproduce the magnitude of the
measured effects and were in general lower. For instance, at 6~nrad,
the calculated emittance growth was 1\%/min, whereas in experiments we
measured 5\%/min.
